---
title: "Lab 9 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
library("here")
library(tidyverse)
```

## Seating
1. If you already have a group, it will be helpful to start sitting next to each other.
2. If you don't have a group, hang tight we are working on it.
3. Please setup your computer as normal for today.

## Warm-up
1. In the data folder there is an epidemiology data set on an outbreak of malaria.
2. `rdt` refers to rapid diagnostic test and they are identified here by age group.
3. Make the data tidy and store them as a new object.
```{r}
#people put in dates differently so pay attention
malaria <- read.csv(here("data", "malaria.csv")) 
malaria
```
```{r}
malaria_long <- malaria %>% 
  pivot_longer(contains("rdt"),
               names_to = "age_class",
               values_to = "cases") 
malaria_long
```

4. Which district had the highest *total* number of cases on July 30, 2020?
```{r}
malaria %>% 
  table("District", "malaria_tot")
```

