---
title: "Lab 10 Homework"
author: "Isaac Yang"
date: "`r Sys.Date()`"
output:
  html_document: 
    theme: spacelab
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Answer the following questions and complete the exercises in RMarkdown. Please embed all of your code and push your final work to your repository. Your final lab report should be organized, clean, and run free from errors. Remember, you must remove the `#` for the included code chunks to run. Be sure to add your name to the author header above. For any included plots, make sure they are clearly labeled. You are free to use any plot type that you feel best communicates the results of your analysis.  

Make sure to use the formatting conventions of RMarkdown to make your report neat and clean!  

## Load the libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(naniar)
``` 

## Desert Ecology
For this assignment, we are going to use a modified data set on [desert ecology](http://esapubs.org/archive/ecol/E090/118/). The data are from: S. K. Morgan Ernest, Thomas J. Valone, and James H. Brown. 2009. Long-term monitoring and experimental manipulation of a Chihuahuan Desert ecosystem near Portal, Arizona, USA. Ecology 90:1708.
```{r}
deserts <- read_csv(here("lab10", "data", "surveys_complete.csv"))
```

1. Use the function(s) of your choice to get an idea of its structure, including how NA's are treated. Are the data tidy? 
```{r}
glimpse(deserts)
```
```{r}
#The NAs are being treated as missing data. It makes sense because the species, ids, and dates are all known, but the data observations may be hard to get or just missing.
naniar::miss_var_summary(deserts)
```
```{r}
#I think that the data is tidy overall. There are no weird values and the rows, columns, and cells all fit the tidy criteria.
deserts <- clean_names(deserts)
deserts
```

2. How many genera and species are represented in the data? What are the total number of observations? Which species is most/ least frequently sampled in the study?
```{r}
#According to the data, there are 34786 observations. (look in environment panel)
deserts %>% 
  count(genus, sort = T)
#There are 26 genera.
```
```{r}
deserts %>% 
  count(species, sort = T)
#There are 40 species, with merriami being the most sampled and clarki, scutalatus, tereticaudus, tigris, uniparens, and virdis being tied for the least sampled.
```

3. What is the proportion of taxa included in this study? Show a table and plot that reflects this count.
```{r}
deserts %>% 
  count(taxa, sort = T)
```
```{r}
#I did did a scale_y_log10 so that the graph wouldn't be so contorted by the rodents.
deserts %>% 
  ggplot(aes(x=taxa))+geom_bar()+scale_y_log10()
```


4. For the taxa included in the study, use the fill option to show the proportion of individuals sampled by `plot_type.`
```{r}
deserts %>% 
  ggplot(aes(x=taxa, fill = plot_type))+geom_bar()+scale_y_log10()
```

5. What is the range of weight for each species included in the study? Remove any observations of weight that are NA so they do not show up in the plot.
```{r}
deserts %>% 
  group_by(species) %>% 
  top_n(1, weight) %>% 
  select(species, weight) %>% 
  arrange(desc(weight))
```
```{r}
deserts %>% 
  group_by(species) %>% 
  top_n(-1, weight) %>% 
  select(species, weight) %>% 
  arrange(desc(weight))
```
```{r}
deserts %>% 
  ggplot(aes(x=species, y= weight))+
  geom_boxplot(na.rm = T)+
  coord_flip()
```

6. Add another layer to your answer from #5 using `geom_point` to get an idea of how many measurements were taken for each species.
```{r}
deserts %>% 
  ggplot(aes(x=species, y= weight))+
  geom_boxplot(na.rm = T)+
  geom_point(na.rm = T)+
  coord_flip()
```


7. [Dipodomys merriami](https://en.wikipedia.org/wiki/Merriam's_kangaroo_rat) is the most frequently sampled animal in the study. How have the number of observations of this species changed over the years included in the study?\
```{r}
deserts %>% 
  filter(species == "merriami" & genus == "Dipodomys") %>% 
  count(year)
```
```{r}
deserts %>% 
  filter(species == "merriami" & genus == "Dipodomys") %>% 
  ggplot(aes(x=year))+geom_bar()
```


8. What is the relationship between `weight` and `hindfoot` length? Consider whether or not over plotting is an issue.
```{r}
#There seems to be a general trend of as hindfood_length increases, the weight increases. It seems to max out a certain value, but the general trend is still there. Over plotting is sort of an issue because so many of these values are overlapping and cluttering up the data.
deserts %>% 
  ggplot(aes(x= hindfoot_length, y= weight))+
  geom_point(na.rm = T)
```

9. Which two species have, on average, the highest weight? Once you have identified them, make a new column that is a ratio of `weight` to `hindfoot_length`. Make a plot that shows the range of this new ratio and fill by sex.
```{r}
deserts %>% 
  select(species, weight) %>%
  group_by(species) %>% 
  summarise(weight_mean = mean(weight, na.rm = T)) %>% 
  arrange(desc(weight_mean))
```
```{r}
deserts %>% 
  filter(species ==  "spectabilis" | species == "albigula")  %>% 
  mutate(weight_to_hindfoot_length = weight/hindfoot_length, na.rm = T) %>% 
  ggplot(aes(x=species, y= weight_to_hindfoot_length, fill = sex))+
  geom_boxplot(na.rm=T)
  
```


10. Make one plot of your choice! Make sure to include at least two of the aesthetics options you have learned.
```{r}
deserts %>% 
  filter(taxa == "Rodent") %>% 
  group_by(year) %>% 
  mutate(rodent_mean_weight = mean(weight, na.rm = T)) %>% 
  ggplot(aes(x= year, y= rodent_mean_weight, fill = sex))+geom_col(position = "dodge")+
   labs(title = "Year vs Mean Rodent Weight",
       x = "Year",
       y = "Mean Rodent Weight")+
   theme(plot.title = element_text(size = rel(1.5), hjust = 0.5))
```

## Push your final code to GitHub!
Please be sure that you check the `keep md` file in the knit preferences. 