---
title: "Lab 6 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Setup
1. Login to the lab computer (please don't use your personal computer).  
2. Navigate to github.com and login.   
2. Use GitHub desktop to clone your repository to the desktop.   
5. Copy the class repository to the desktop (https://github.com/jmledford3115/datascibiol).  
6. Copy the files for today's lab from the class repository and paste them into **your** repository.  
7. Open today's lab in RStudio.  

## Review from last time
### *With a partner, discuss the following questions*
1. What is a pipe? Why are they useful in R?
2. What is the shortcut for making a pipe?
3. What is the difference between `select`, `filter`, and `mutate`?
4. What are the logistics of midterm 1?

### Warm-up
1. Open the data `ecs21351-sup-0003-SupplementS1.csv`
```{r}
library(tidyverse)
library(janitor)
```

```{r}
ecs_data <- readr::read_csv("data/ecs21351-sup-0003-SupplementS1.csv", skip = 2)
```

2. Clean the names of the variables
```{r}
ecs_data <- ecs_data %>% clean_names
```

3. Explore the data using a function of your choice
```{r}
glimpse(ecs_data)
```

4. Are there more veggie, omni, insecivore, or nectar feeders in the data?

There are more omnivores.
```{r}
table(ecs_data$diet)
```

5. Which families are Veggie?
 Anatidae   Phasianidae      Rallidae Tetraodonidae 
```{r}
new_data <-filter(ecs_data, diet == "Vegetation")
table(new_data$family)

```

